\documentclass[11pt]{article}

\usepackage{lscape,color}

\topmargin -0.75truein
\oddsidemargin -0.4truein
\textheight 9.25truein
\textwidth 6.7truein
\hbadness=10001
\hfuzz=200pt


\begin{document}
%\input dspace12.tex
%\input pstricks.tex
%\input psfig
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}
\newcommand{\bt}{\begin{tabbing}}
\newcommand{\et}{\end{tabbing}}
\newcommand{\eg}{{\it e.g.~}}
\newcommand{\ie}{{\it i.e.~}}
\newcommand{\ul}{\underline}
\newcommand{\axaf}{{\em AXAF}}
\def\la{\hbox{\rlap{$<$}\lower0.5ex\hbox{$\sim$}\ }}


\large
%\vspace*{-0.5in}
\centerline {\bf 4.31\_V2.6 TURN OFF DEA B  }
\vspace{0.25in}

\normalsize
\noindent{\it Last Revised: October 17, 2017}\\
\noindent{\bf Filename: deab\_off} \\


\noindent {\bf BRIEF FUNCTIONAL DESCRIPTION:} \\
\normalsize
This is an ``atomic'' procedure which simply turns off the DEA side B.
It should be safe to execute under any condition except a spacecraft
power or thermal emergency.


\vspace{0.25in}
\noindent The sequence of actions will be:
\be
\item Power down all the video boards
\vspace{-0.10in}
\item  Turn off and disable DEA power supply side B
\ee


\vspace{0.15in}
\normalsize
\noindent {\bf ASSUMED INSTRUMENT STATE:} 
\normalsize
\be
\item Assumes that the PSMC has power from the spacecraft.
\vspace{-0.10in}
\item The instrument should not be executing a science run.
\vspace{-0.10in}
\item The instrument should not be in bakeout mode. (See details below.)
\vspace{-0.10in}
\item Assumes that at least one side of the DPA is powered and that a BEP is active
and ready to execute commands. If not, skip Step 1, which issues the WSVIDALLDN
command to the BEP.
\ee

%\vspace{0.25in}
\normalsize
\noindent {\bf SPECIAL INITIAL CONDITIONS:} \\
\normalsize

%\vspace{0.25in}
\normalsize
\noindent {\bf OPERATIONAL CONSTRAINTS/CAUTIONS:} \\
\normalsize

The DEA power status is normally indicated by the values of the 1DEPSA and
1DEPSB flags, which should not both be 1 simultaneously.
However, if neither side of the DPA is receiving power
({\it i.e.}, if 1DPP0AVO and 1DPP0BVO are simultaneously reading $0.0 \pm 0.5$ V),
the DEA flag values will be unreliable and the DEA voltage
channels (1DEP[0123][AB]VO) should instead be used to determine which
sides of the DEA are powered).

If neither side of the DPA is receiving power, then the command to power down the
video boards should be skipped.

Typically 1DEICBCU (and likewise the A-side 1DEICACU) reads 16-−18~A when
unpowered. This is a feature of all TDB versions up through v14 and is
not an anomaly.

The instrument should not be executing a science run using DEA side B.
If power is removed from DEA side B while a science run is in progress, the science
run will terminate abnormally.
The data will still be useful, but the processing will be more complicated.

The instrument should not be in bakeout mode. If the DEA side B power is
removed during a bakeout, the FP bakeout heater will lose power and the bakeout of
the FP will terminate. The DH bakeout heater is unaffected by a power loss to the
DEA and will therefore still be executing a bakeout if power is lost to the DEA.



\vspace{0.15in}
\normalsize
\noindent {\bf REFERENCES:} \\
\normalsize

\normalsize
\noindent {\bf CHANGE HISTORY:} \\
\normalsize

{\bf V1.0}
\begin{itemize}
\item Initial version based on deaa\_off
\end{itemize}

{\bf V1.1}
\begin{itemize}
\item Minor edits; for ACIS team review
\end{itemize}

{\bf V2.0}
\begin{itemize}
\item For FOT review
\end{itemize}

{\bf V2.1}
\begin{itemize}
\item Moved telemetry checks to step 1.1
\end{itemize}

{\bf V2.2}
\begin{itemize}
\item Removed check of 1DEICBCU
\end{itemize}

{\bf V2.3}
\begin{itemize}
\item Altered wording to conform to A side procedure
\item Replaced Constraints/Cautions section from A side procedure
\item Added step to power down video boards (in both table and brief functional description)
\item Reordered telemetry checks to match web page; added input voltage check
\end{itemize}

{\bf V2.4}
\begin{itemize}
\item Added language stating that if the DPA is unpowered, the WSVIDALLDN command
should not be issued.
\end{itemize}

{\bf V2.5}
\begin{itemize}
\item Clarified language per PGF comments
\end{itemize}

{\bf V2.6}
\begin{itemize}
\item Fixed errors on voltages
\end{itemize}

\newpage\
\vspace{0.4\textheight}
\bc This page is intentionally blank \ec

\newcommand{\tablecaptiontext}{TURN OFF DEA B}
\input{deab_off.tab}

\end{document}
